\begin{thebibliography}{99}

\bibitem{lib:bachmann} Bachmann O., Schoenemann H. Monomial Representations for Groebner Basis Computation. \textit{Proc. International Symposium on Symbolic and Algebraic Computation}, ACM 1998

\bibitem{lib:bernstein} Bernstein D. Pippenger's Exponentiation Algorithm.\\ \verb|http://cr.yp.to/papers.html#pippenger|

\bibitem{lib:pan_rec} Bini D., Pan V. Parallel polynomial computations by recursive processes. \textit{Proc. ACM SIGSAM Intern. Symp. on Symbolic and Algebraic Comp.}, ACM 1990

\bibitem{lib:pan_par} Bini D., Gemignani L., Pan V. Improved parallel computations with matrices and polynomials. \textit{Proc. 18-th Intern. Symposium on Automata, Languages and Programming}, Springer 1991, 520-531

\bibitem{lib:bos95} Bos J., Coster M. Addition chain heuristics. \textit{Proc. CRYPTO’89}, Springer 1995

\bibitem{lib:brauer} Brauer, O.M. Addition-Subtraction Chains. \textit{Diplomarbeit}, University Paderborn 2001

\bibitem{lib:cortes} Cruz-Cortes N., Rodriges-Henriques F., Jurez Morales R., Coello C. Finding optimal addition chains using a genetic algorithm approach. \verb|http://delta.cs.cinvestav.mx/~francisco/cis2005_nareli.pdf|, 2005

\bibitem{lib:dimitrov} Dimitrov V.S., Jullien G.A., Miller W.C. Algorithms for multiexponentiation based on complex arithmetic. \textit{Proc. 13th Symposium on Computer Arithmetic}, IEEE 1997

\bibitem{lib:downey} Downey P., Leong B., Sethi R. Computing sequences with addition chains. \textit{SIAM Journal on Computing 10 (3)}, SIAM 1981, 638–646

\bibitem{lib:gordon97} Gordon D. A survey of fast exponentiation methods. \textit{Journal of Algorithms 27}, Elsevier 1998, 129-146

\bibitem{lib:knuth} Knuth D. The Art of Computer Programming, vol. 2. Addison-Wesley 1981

\bibitem{lib:knuthpoly} Knuth D. Evaluation of Polynomials by Computer. \textit{Communications of the ACM, vol. 5, issue 12}, ACM 1962, 595-599

\bibitem{lib:moeller} Moeller B. Algorithms for Multiexponentiation. \textit{Technical report}, TU Darmstadt 2001

\bibitem{lib:olivos} Olivos J. On vectorial addition chains. \textit{Journal of Algorithms}, Elsevier 1981, 13-21

\bibitem{lib:vasiliev_complex} Vasiliev N.N. Complexity of monomial evaluations and duality. \textit{Computer Algebra in Scientifig Computing}, Springer 1999, 479-485

\bibitem{lib:vasiliev_cade09} Vasiliev N.N. Fast polynomial reduction. \textit{Proc. Workshop on Computer Algebra and Differential Equations}, 2009 

\bibitem{lib:vasiliev_jointeval} Vasiliev N.N. Joint Evaluations of Sparse Polynomials and the Synthesis of Evaluating Programms. \textit{Proc. International Conference Systems and Methods of Analytical Computations with Computers in Theor. Phys.}, 1985, 154-159

\bibitem{lib:vasiliev_notes} Vasiliev N.N. Creation of efficient symbolic-numeric interface. \textit{Lecture Notes in Computer Science V378}, Springer 1989, 118-119

\bibitem{lib:vasiliev_sprint} Vasiliev N.N. The System for the Synthesis of evaluating programms for polynomial-trigonometric expressions. \textit{Proc. International Conference Analytical Computations with Computers in Theor. Phys.}, 1983, 120-124

\bibitem{lib:zobnin} Александров Д.Е., Галкин В.В., Зобнин А.И., Левин М.В. Распараллеливание матричных алгоритмов вычисления базисов Грёбнера. \textit{Фундаментальная и прикладная математика, 2008, том 14, № 4}, МГУ 2008, 35—64

\bibitem{lib:ahoullman} Ахо А., Хопкрофт Дж., Ульман Дж. Построение и анализ вычислительных алгоритмов, Москва, Мир 1979

\bibitem{lib:belaga} Белага Э.Г. О вычислении значений многочленов от одного переменного с предварительной обработкой коэффициентов. \textit{Проблемы кибернетики, вып. 5. М.}, Физматлит 1961, 7-16

\bibitem{lib:kliskunov} Клискунов А.Н. Эффективные вычисления нормальных форм в алгоритме Бухбергера. \textit{Магистерская диссертация}, СПбГПУ ФизМех, 2006

\bibitem{lib:cox} Кокс Д., Литтл Дж., О`Ши Д. Идеалы, многообразия и алгоритмы. Москва, Мир 2000

\bibitem{lib:kochergin} Кочергин В.В. Об асимптотике сложности аддитивных вычислений систем целочисленных линейных форм, \textit{Дискретный анализ и исследование операций, Апрель-Июнь 2006. Серия 1. Том 13, № 2}, 38–58

\bibitem{lib:kochergin_degs} Кочергин В.В. О вычислении наборов степеней, \textit{Дискретная математика, том 6, выпуск 2}, 1994, 129-137

\bibitem{lib:pan_schemes} Пан В.Я. Некоторые схемы для вычисления многочленов с действительными коэффициентами. \textit{Проблемы кибернетики, вып. 5. М., Физматлит}, 1961, 17-30

\bibitem{lib:axiom} Axiom: the scientific computation system. \verb|http://www.axiom-developer.org/|

\bibitem{lib:gmp} The GNU multiple precision arithmetic library. \verb|http://gmplib.org/|

\bibitem{lib:indigo} Indigo API. \verb|http://opensource.scitouch.net/indigo/|

\bibitem{lib:maple} Maple, computer algebra system. \verb|http://www.maplesoft.com/|

\bibitem{lib:singular} Singular, computer algebra system. \verb|http://www.singular.uni-kl.de/|

\bibitem{lib:sage} Sage, open-source mathematics software systems. \verb|http://www.sagemath.org/|

\bibitem{lib:sanpin} Гигиенические требования к персональным электронно-вычислительным машинам и организации работы. СанПин 2.2.2/2.4.1340-03.

\end{thebibliography}




